Augmentation of a Model Historical Harpsichord Mechanism for Haptic Enabled Interaction

### 2025-01-18 src/main.tex
format abstract

%%
%% This is file `sample-nime-paper.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `all,proceedings,bibtex,sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-nime-paper.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% History of NIME Template Updaters:
%% Modified by Florent Berthaut, Charles Martin, Yichen Wang, 21 November 2024
%% Modified by Adnan Marquez-Borbon 30 November 2022
%% Modified by Courtney Reed 28 November 2022
%% Modified by Joe Wright 14 December 2019
%% Modified by Niccolò Granieri 10 October 2018
%% Modified by Angelo Fraietta 23 December 2018
%% Modified by Angelo Fraietta 22 November 2018
%% Modified by Rodrigo Schramm on 22 September 2018
%% Modified by Luke Dahl on 17 October 2-17
%% Modified by Cumhur Erkut on <2016-10-11 Tue>
%% Modified by Edgar Berdahl on 5 November 2014
%% Modified by Baptiste Caramiaux on 25 November 2013
%% Modified by Kyogu Lee on 7 October 2012
%% Modified by Georg Essl on 7 November 2011
%%
%% And here's the template:
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{nimeart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{nimeart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[sigconf,anonymous]{nimeart}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
This work describes the design of an electronically augmented replica of a 16th-century harpsichord keyboard with a typical Renaissance Italian layout. The keyboard is a collaboration between the authors and the Museo di San Colombano, which houses the Tagliavini Collection of playable historical keyboard instruments. The keyboard was commissioned for exhibition purposes and to enhance the experiential authenticity of the collection. The keyboard emulates the mechanics of a two-register harpsichord featuring a single manual. Unpitched strings under tension replicate the mechanical resistance characteristic of the original compass. An array of infrared LED/phototransistor pairs, connected to a microcontroller, was installed within the interface to generate a continuous stream of data corresponding to the jacks' motion. This paper details the design principles, development process, open-source implementation, and realisation of the installation for the San Colombano exhibition.
\end{abstract}

@@

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{images/side_w-o_sensors.png}
  \caption{3-key Model Harpsichord Mechanism by Graziano Bandini, Bologna 2023}
  \Description{3-key Model Harpsichord Mechanism by Graziano Bandini, Bologna 2023}
  \label{fig:teaser}
\end{teaserfigure}

>>>>

%%
%% This is file `sample-nime-paper.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `all,proceedings,bibtex,sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-nime-paper.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% History of NIME Template Updaters:
%% Modified by Florent Berthaut, Charles Martin, Yichen Wang, 21 November 2024
%% Modified by Adnan Marquez-Borbon 30 November 2022
%% Modified by Courtney Reed 28 November 2022
%% Modified by Joe Wright 14 December 2019
%% Modified by Niccolò Granieri 10 October 2018
%% Modified by Angelo Fraietta 23 December 2018
%% Modified by Angelo Fraietta 22 November 2018
%% Modified by Rodrigo Schramm on 22 September 2018
%% Modified by Luke Dahl on 17 October 2-17
%% Modified by Cumhur Erkut on <2016-10-11 Tue>
%% Modified by Edgar Berdahl on 5 November 2014
%% Modified by Baptiste Caramiaux on 25 November 2013
%% Modified by Kyogu Lee on 7 October 2012
%% Modified by Georg Essl on 7 November 2011
%%
%% And here's the template:
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{nimeart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{nimeart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[sigconf]{nimeart}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
This work describes the design of an electronically augmented replica of a
16th-century harpsichord keyboard with a typical Renaissance Italian layout. The
keyboard is a collaboration between the authors and the Museo di San Colombano,
which houses the Tagliavini Collection of playable historical keyboard
instruments. The keyboard was commissioned for exhibition purposes and to
enhance the experiential authenticity of the collection. The keyboard emulates
the mechanics of a two-register harpsichord featuring a single manual. Unpitched
strings under tension replicate the mechanical resistance characteristic of the
original compass. An array of infrared LED/phototransistor pairs, connected to a
microcontroller, was installed within the interface to generate a continuous
stream of data corresponding to the jacks' motion. This paper details the design
principles, the development, open source implementation, and execution of
the installation for the San Colombano exhibition.
\end{abstract}

@@

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{images/49-key-front.png}
  \caption{49-key Model Harpsichord Mechanism by Roberto Livi, Bologna 2024}
  \Description{49-key Model Harpsichord Mechanism by Roberto Livi, Bologna 2024}
  \label{fig:teaser}
\end{teaserfigure}

% \begin{teaserfigure}
%   \includegraphics[width=\textwidth]{images/side_w-o_sensors.png}
%   \caption{3-key Model Harpsichord Mechanism by Graziano Bandini, Bologna 2023}
%   \Description{3-key Model Harpsichord Mechanism by Graziano Bandini, Bologna 2023}
%   \label{fig:teaser}
% \end{teaserfigure}
